Linear Ordered Attribute Grammar scheduling using SAT-solving

### 2014-10-18 paper/paper.tex
Add a ref to Bryant in the discussion as well.

In the translation into the SAT-problem we have used a novel technique for ruling out cycles in the SAT problem using chordal graphs. This technique makes the problems much smaller than directly ruling out cycles, while encoding the same restrictions. We believe that this technique is applicable in other problems using SAT-solvers as well.

>>>>

In the translation into the SAT-problem we have used a novel technique for ruling out cycles in the SAT problem using chordal graphs. The technique was inspired by existing work on chordility for expressing equality logic \cite{bryant-chordal}. Using chordal graphs makes the problems much smaller than directly ruling out cycles, while encoding the same restrictions. We believe that this technique is applicable in other problems using SAT-solvers as well.
